Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-05-02 supp_mat_complexity_selection.Rmd
playing around with adjust smooth to get sensical curves.

## Gall Height
gam_red.control_size <- gam(gall_survival ~
                             s(c.Gall_Height_mm) + 
                             c.gall_individuals +
                             c.Density_per_100_shoots,
                           data = control_df, family = binomial(link = "logit"))
summary(gam_red.control)

gam.plot(gam_red.control)
gam.plot(gamm_red.control$gam)

@@

gam_red.control_density <- gam(gall_survival_mean ~
                                c.Gall_Height_mm_mean + 
                                c.gall_individuals_mean +
                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.control_density)

@@

@@

gam_red.treatment_density <- gam(gall_survival_mean ~
                                c.Gall_Height_mm_mean + 
                                c.gall_individuals_mean +
                                s(c.Density_per_100_shoots),
                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.treatment_density)

>>>>

## Gall Height
gam_red.control_size <- gam(gall_survival ~
                             s(c.Gall_Height_mm) + 
                             c.gall_individuals +
                             c.Density_per_100_shoots,
                           data = control_df, family = binomial(link = "logit"))
summary(gam_red.control_size)

gam.plot(gam_red.control_size)
gam.plot(gamm_red.control$gam)

@@

test.control_df_plant.level <- control_df %>%
  group_by(Treatment.focus, Plant_Position) %>%
  summarise(gall_survival_mean = mean(gall_survival),
            gall_sample_size = n(),
            gall_individuals_mean = mean(gall_individuals),                 
            Gall_Height_mm_mean = mean(Gall_Height_mm),
            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
  ungroup() %>%
  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

gam_red.control_density <- gam(gall_survival_mean ~
                                s(c.Gall_Height_mm_mean) + 
                                s(c.gall_individuals_mean, k=3) +
                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
                             data = control_df_plant.level,
                             family = binomial, #(link = "logit"), 
                             weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.control_density)
plot(gam_red.control_density, pages=1, residuals=TRUE)
gam.check(gam_red.control_density)

plot(lambda, gcvscore, type = "l") # or
plot(log(lambda), gcvscore, type = "l")

@@

set.seed(1) 
dat <- gamSim(1,n=400,scale=2)

## fit a GAM with quite low `k'
b<-gam(y~s(x0,k=6)+s(x1,k=6)+s(x2,k=6)+s(x3,k=6),data=dat)
plot(b,pages=1,residuals=TRUE) ## hint of a problem in s(x2)
gam.check(b)

@@

gam_red.treatment_density <- gam(gall_survival_mean ~
                                s(c.Gall_Height_mm_mean) + 
                                s(c.gall_individuals_mean) +
                                s(c.Density_per_100_shoots),
                             data = treatment_df_plant.level, family = binomial(link = "logit"))#, weights = gall_sample_size) # weighting appears to alter the results...
summary(gam_red.treatment_density)
